---
format: 
  html:
    toc: true
    toc-depth: 4
---
```{r echo = FALSE, message = FALSE}

library(tidyverse)
library(xfun) # numbers_to_words function
library(lubridate)

data <- read.csv("data/2023_annualreportdata.csv")

  data$FirstVisit <- as_date(data$FirstVisit)
  data$FirstVisit <- paste(month(data[,"FirstVisit"], 
                           label = TRUE, abbr = FALSE), 
                           day(data[,"FirstVisit"]), 
                           sep = " ")
  data$LastVisit <- as_date(data$LastVisit)
  data$LastVisit <- paste(month(data[,"LastVisit"], 
                          label = TRUE, abbr = FALSE), 
                          day(data[,"LastVisit"]), 
                          sep = " ")

```

# U.S. Forest Service 

## Region 1  

### Region 1 National Forests 
 
```{r, echo = FALSE, message = FALSE}

# USFS-Region 1 National Forests is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "USFS-Region 1 National Forests")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Beaverhead-Deerlodge National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Beaverhead-Deerlodge National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Bitterroot National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Bitterroot National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Clearwater National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Clearwater National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Custer National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Custer National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Flathead National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Flathead National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Gallatin National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Gallatin National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Helena National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Helena National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Idaho Panhandle National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Idaho Panhandle National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Kootenai National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Kootenai National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Lewis and Clark National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Lewis and Clark National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Lolo National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Lolo National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Nez Perce National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Nez Perce National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::



### Region 1 National Grasslands 
 
```{r, echo = FALSE, message = FALSE}

# USFS-Region 1 National Grasslands 2013-Present is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "USFS-Region 1 National Grasslands 2013-Present")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# ND-BCR17-MG is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "ND-BCR17-MG")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# ND-BCR17-RG is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "ND-BCR17-RG")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# SD-BCR17-RG is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "SD-BCR17-RG")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::


## Region 2 

### Region 2 National Forests 
 
```{r, echo = FALSE, message = FALSE}

# USFS-Region 2 National Forests is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "USFS-Region 2 National Forests")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# CO-BCR16-AR is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "CO-BCR16-AR")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# WY-BCR10-BI is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "WY-BCR10-BI")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Black Hills National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Black Hills National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# CO-BCR16-GM is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "CO-BCR16-GM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Medicine Bow National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Medicine Bow National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Nebraska National Forests is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Nebraska National Forests")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# CO-BCR16-PS is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "CO-BCR16-PS")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Rio Grande National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Rio Grande National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Routt National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Routt National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# CO-BCR16-SA is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "CO-BCR16-SA")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Shoshone National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Shoshone National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# White River National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "White River National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::



### Region 2 National Grasslands 
 
```{r, echo = FALSE, message = FALSE}

# USFS-Region 2 National Grasslands 2013-Present is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "USFS-Region 2 National Grasslands 2013-Present")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Nebraska National Grasslands is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Nebraska National Grasslands")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# KS-BCR18-CM is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "KS-BCR18-CM")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# CO-BCR18-CO is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "CO-BCR18-CO")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# CO-BCR18-PG is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "CO-BCR18-PG")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# WY-BCR17-TB is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "WY-BCR17-TB")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::


## Region 3 

### Region 3 National Forests 
 
```{r, echo = FALSE, message = FALSE}

# Coronado National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Coronado National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Kaibab National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Kaibab National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::


## Region 4 

### Region 4 National Forests 
 
```{r, echo = FALSE, message = FALSE}

# USFS-Region 4 National Forests is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "USFS-Region 4 National Forests")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Ashley National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Ashley National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Boise National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Boise National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Bridger-Teton National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Bridger-Teton National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Caribou-Targhee National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Caribou-Targhee National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Dixie National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Dixie National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Fishlake National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Fishlake National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Humboldt-Toiyabe National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Humboldt-Toiyabe National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Manti-La Sal National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Manti-La Sal National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# ID-BCR10-PA is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "ID-BCR10-PA")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Salmon-Challis National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Salmon-Challis National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Sawtooth National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Sawtooth National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

```{r, echo = FALSE, message = FALSE}

# Uinta-Wasatch-Cache National Forest is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "Uinta-Wasatch-Cache National Forest")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::




```{r, echo = FALSE, message = FALSE}

# ID-BCR9-CU is a special value from the heddlr_loop.qmd file
x <- which(data$stratum == "ID-BCR9-CU")

name <- data[x, "name"]
compilation <- ifelse(data[x, "Strata"] > 1, "compiling and jointly", "compiling and")
n.strata <- if (data[x, "Strata"] <= 10) {numbers_to_words(data[x, "Strata"])
  } else data[x, "Strata"]
stratum_plural <- ifelse(data[x, "Strata"] > 1, "strata", "stratum")
completed.grids <- (data[x, "CompletedGrids"])
planned.grids <- (data[x, "PlannedGrids"])
percent.completed <- round((completed.grids/planned.grids)*100)

transect.clause <- if (planned.grids == completed.grids & planned.grids > 2) {
  paste("all")
  } else if (planned.grids == completed.grids & planned.grids == 2) {paste("both")
  } else {paste((completed.grids), 
             "of", 
             (planned.grids),
             sep = " ")}

year <- data[x, "Year"]
completed.points <- data[x, "CompletedPoints"]
first.visit <- data[x, "FirstVisit"]
last.visit <- data[x, "LastVisit"]
n.species <- data[x, "nBirdSpecies"]
n.priority <- data[x, "nPriority"]
n.density <- data[x, "DensitySpeciesCount"]
n.density.priority <- data[x, "DensityPrioritySpecies"]
n.density.robust <- data[x, "DensityRobustCV"]
n.occupancy <- data[x, "OccupancySpeciesCount"]
n.occupancy.priority <- data[x, "OccupancyPrioritySpecies"]
n.occupancy.robust <- data[x, "OccupancyRobustCV"]
type <- if (data[x, "is_superstratum"]) {"Superstratum"} else {"Stratum"}
super_stratum <- if (data[x, "is_superstratum"]) {data[x, "stratum"]} else {data[x, "LongStratum"]}

p1 <- str_glue("We obtained results for {name} by {compilation} analyzing data from {n.strata} {stratum_plural}.")

p2 <- str_glue("Field technicians completed {transect.clause} planned surveys ({percent.completed}%) in {year}. Technicians conducted {completed.points} point counts within the {completed.grids} surveyed grid cells between {first.visit} and {last.visit}. They detected {n.species} bird species, including {n.priority} priority species.")

p3 <- str_glue("Bird Conservancy estimated densities and population sizes for {n.density} species that were detected in any year during which surveys were conducted, {n.density.priority} of which are priority species. The data yielded robust density estimates (CV < 50%) for {n.density.robust} species.")

p4 <- str_glue("Bird Conservancy estimated the proportion of 1 km² grid cells occupied (Ψ, Psi) throughout {name} for {n.occupancy} species that were detected in any year during which surveys were conducted, {n.occupancy.priority} of which are priority species. The data yielded robust occupancy estimates (CV < 50%) for {n.occupancy.robust} species.")

p5 <- str_glue("To view a map of survey locations, density, occupancy, & trend results and species counts within {name} across all years of the project, visit the [RMADC](https://bird-conservancy.shinyapps.io/rmadc/).")

head <- paste("####", name, sep = " ")

```

`r head`

`r p1`

`r p2`

`r p3`

`r p4`

::: {.callout-note appearance="minimal"}
## View results on the Rocky Mountain Avian Data Center
`r p5`  

On the Explore the Data tab, select **`r super_stratum`** from the **`r type`** drop-down filter.
:::

